Modeling Intervention Strategies for United States Tuberculosis Control

### 2014-03-02 in_progress/presentations/paper/draftOld.tex

\title{Modeling Intervention Strategies for United States TB Control}
\begin{document}
\maketitle

\section{Abstract}
An extended epidemiological model for Tuberculosis in the US was developed,
based on an existing epidemiological model developed in 2012 by the Centers for
Disease Control and Prevention.  Economic parameters to track the cost burden of
TB for the US health care system were added.  The sensitivity of the extended
model to changes in parameters was analyzed, and the percentage of foreign-born
immigrants with LTBI appears to be a highly influential parameter in the model.
Intervention strategies to reduce LTBI among foreign-born arrivals were
evaluated, and estimates of the cost per case averted were found. Additionally,
a population-level, stochastic, agent-based model was built to provide
statistical verification of the results of the deterministic model and to
demonstrate feasibility of agent-based modeling even on such large population
scales.

>>>>

\title{Modeling Intervention Strategies for United States Tuberculosis Control}
\begin{document}
\maketitle

\section{Abstract}
An extended epidemiological model of tuberculosis in the United States was developed,
based on an existing model developed in 2012 by the Centers for
Disease Control and Prevention.  Economic parameters to track the cost burden of
tuberculosis for the United States health care system were added.  The sensitivity of the extended
model to changes in parameters was analyzed, and the percentage of foreign-born
immigrants with latent tuberculosis infection appears to be a highly influential parameter
 in the model. Intervention strategies to reduce latent tuberculosis infection among foreign-born arrivals were evaluated, and estimates of the cost per case averted were found. Additionally,
a population-level, stochastic, agent-based model was built to provide
statistical verification of the results of the deterministic model and to
demonstrate feasibility of agent-based modeling even on such large population
scales.
